### 2017-03-30 paper/evaluation.tex
Adjusted vspace and deleted unnecessary comment in RQ1
updated RQ1

\Comment{\Jbc{Ensure to describe that: subjects that could not run the tests
due to incompatible testing environment were removed (likely to happen
for subjects that rely on database systems and other external
factors), the exit status for all executions are consistent and I
removed flaky projs}}

@@

\Jbc{these results will be updated $\rightarrow$} It is important to
mention that Figure~\ref{fig:rq1-barplot} represents a lower bound
estimation for time cost because some tests may finish earlier than
expected due to existing bugs on the ongoing revision.  From the
\numSubjs{} compiled projects, \numSubjsPass{} successfully executed
all tests and \numSubjsFail{} reported test failures.  Also, some
projects omit long-running tests on their default execution. For
instance, it is necessary to invoke Maven with additional parameters
to run integration tests from project \CodeIn{apache.maven-surefire}
(nearly 30 min in our environment).

>>>>

@@

It is important to mention that Figure~\ref{fig:rq1-barplot}
represents a lower bound estimation for time cost because some tests
may finish earlier than expected due to existing bugs on the ongoing
revision.  From the \numSubjs{} compiled projects, \numSubjsPass{}
successfully executed all tests and \numSubjsFail{} reported test
failures.  Also, some projects may omit long-running tests on their
default execution. For instance, the project
\CodeIn{apache.maven-surefire} runs all unit tests in a few seconds in
our environment.  According to our criteria, this project would be
classified as \shortg{} but we noticed that by providing additional
parameters from the subject, the integration tests are included during
the execution.  After including the integration tests, the tests time
increases to nearly 30 minutes.  Since it would be impractical to
analyze each project, we considered only the tests executed by
default.
